Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-21 ms.tex
more clean up and reorganization

\subsection{Smoothing}
We wish to simultaneously fit \verb|i100| along with four \PLANCK~bands. To 
properly combine these maps, they must have the same point spread function 
(PSF). \verb|i100|, with its $6.1'$ symmetric Gaussian PSF, is the 
lowest-resolution map we have included. To match PSFs, we have therefore 
smoothed each of the \PLANCK~maps under consideration to $6.1'$ resolution by 
considering each native map to have a symmetric Gaussian beam and smoothing by 
the appropriate symmetric Gaussian such that the resulting map has a FWHM of 
$6.1'$. The FWHM we assign to the native \PLANCK~maps is taken from 
\cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.

\subsection{CMB Removal}
The CMB is effectively imperceptible in \PLANCK~857 GHz, but can be noticed at 
a low level in \PLANCK~545 GHz, and is prominent in \PLANCK~217 GHz and 353 
GHz relative to the diffuse Galactic emission we wish to characterize, 
especially at high latitudes. To remove the CMB anisotropies, we have 
subtracted the SMICA model from each of the relevant \PLANCK~maps 
\citep{smica}, after appropriate unit conversions. Removal of the residual 
Solar dipole at low frequencies is discussed in $\S$\ref{sec:zp}.

\subsection{Compact Sources}
To mask compact sources, we use the SFD compact source mask, which was 
originally constructed to mask point sources and resolved compact objects
that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
the maps used in this analysis and do not see any evidence that this compact 
source mask fails to adequately mask compact sources in the \PLANCK~data. In 
practice, we perform our dust SED fits in all pixels, even those flagged by 
the point source mask. Compact source affected pixels can be ignored or 
interpolated over downstream.
%maybe say that we're releasing a version of the map with point sources
%interpolated over by us as well

>>>>

%maybe one sentence here stating that the goal of next few subsections
%is to isolate Galactic thermal dust emission

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
In preparing the \PLANCK~maps for thermal dust SED fitting, we first addressed
the CMB anisotropies before performing any of the interpolation/smoothing 
described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. The CMB anisotropies are 
effectively imperceptible in \PLANCK~857 GHz, but can be perceived at a low 
level in \PLANCK~545 GHz, and are prominent in \PLANCK~217 GHz and 353 GHz 
relative to the Galactic emission we wish to characterize, especially at high 
latitudes. To remove the CMB anisotropies, we have subtracted the Spectral 
Matching Independent Component Analysis (\verb|SMICA|) model from each of the 
\PLANCK~maps \citep{smica}, after applying appropriate unit conversions. 
Removal of the residual Solar dipole at low frequencies is discussed in 
$\S$\ref{sec:zp}.
% SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz

\subsection{Compact Sources}
\label{sec:ptsrc}
To mask compact sources, we use the SFD compact source mask, which was 
originally constructed to mask point sources and resolved compact objects
that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
the maps used in this analysis and do not see any evidence that this compact 
source mask fails to adequately mask compact sources in the \PLANCK~data. In 
practice, we perform our dust SED fits in all pixels, even those flagged by 
the point source mask. Compact source affected pixels can be ignored or 
interpolated over downstream.
%maybe say that we're releasing a version of the map with point sources
%interpolated over by us as well

\subsection{Smoothing}
\label{sec:smth}
We wish to simultaneously fit \verb|i100| along with the four 
highest-frequency \PLANCK~bands. To properly combine these maps, they must have
 the same point spread function (PSF). \verb|i100|, with its $6.1'$ symmetric 
Gaussian PSF, is the lowest-resolution map we have included. To match PSFs, we 
have therefore smoothed each of the \PLANCK~maps under consideration to $6.1'$ 
resolution by considering each native map to have a symmetric Gaussian beam and
 smoothing by the appropriate symmetric Gaussian such that the resulting map 
has a FWHM of $6.1'$. The FWHM we assign to the native \PLANCK~maps is taken 
from \cite{planckbeam}, specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, 
$4.84'$ for 545 GHz, and $4.63'$ for 857 GHz.
